%
% Chapter 6
%
\chapter{Work Plan}\label{chap:work-plan}
\paragraph{}

The following chapter, as we see in the Table~\ref{tab:work-plan}  outlines the detailed work plan for the project since the begin until the end specifying the tasks, durations and timelines.
This structured approach ensured that all aspects of the project were addressed methodically and within the stipulated timeframe, with some adjustments made as the necessary within
the evolution of the project.

\section{Inital Planning and Research (16th February – 28th February)}
\paragraph{}

The project commenced on the 16th of February, with an initial two-week period dedicated to studying the frontend framework to be utilized.
We chose \textbf{Expo React Native} as described in Section~\ref{sec:mobile-application} of Chapter~\ref{chap:architecture}.
This period allowed us to familiarize ourselves with the framework and its features, laying a solid foundation for the frontend development phase.

Following this, another two-week period was dedicated to explore \textbf{Smart Contracts} technology and \textbf{Solidity} programming language.
Solidity is the primary language for writing smart contracts on the Ethereum blockchain, and understanding its syntax and capabilities was crucial for
the later stages of smart contract implementation.

\section{Proposal Development and Structural Decisions (6th March – 29th March)}
\paragraph{}

In early March, we focused on drafting the project proposal. This document outlined the project scope, objectives, and the
technologies to be utilized. This phase was crucial in defining the project's direction and ensuring all team members were aligned on the project's goals.

By mid-March, decisions were made regarding the system's architecture and relational model. These decisions were fundamental as they influenced the project's design
and application's functionality. Following the structural decisions, a one-week period was dedicated to developing a mockup of the application's user interface (UI)
using \textbf{Figma}. This provided a visual representation of the user interface and user experience.

\section{Application Development (5th April – 20th April)}
\paragraph{}

The initial phase of application development commenceed on the 5th of April, with a two-week period dedicated to implementing the application's screens.
This phase involved `translating' the Figma mockup into actual code, using Expo React Native.

Withing the same period, the smart contract development phase commenced. These contracts are essential for the project as they insert
all the certificates into the blockchain and verify the authenticity of the certificates.

\section{Focus Shift to Beta Report (30th April – 2nd June)}
\paragraph{}

As we progressed, it became apparent and recomended by the supervisors that a significant focus should be placed towards the project report.
Therefore, the implementation of smart contracts was temporarily paused.
At the same time, the poster was beeing designed.

\section{Work to Do (3rd June – 30th June)}
\paragraph{}

After the submission of the Beta Report the group will continue the development of the mobile application and the smart contracts.
The main focus ate the first two-week period of June will be the implementation of the smart contracts. After that, the focus will shift to the mobile application
integration with the smart contracts, integration and usability testing and continously updating the project report.

\begin{table}[h]\label{tab:work-plan}
    \centering
    \begin{tabular}{|c|c|p{8cm}|}
        \hline
        \textbf{Initial Date} & \textbf{Duration (weeks)} & \textbf{Description}                                                               \\
        \hline
        16th February         & 2                         & Studying \textit{Expo React Native}                                                \\
        \hline
        28th February         & 2                         & Studying \textit{Smart Contracts} and \textbf{Solidity}                            \\
        \hline
        6th March             & 2                         & Drawing up the Proposal                                                            \\
        \hline
        18th March            & 2                         & Deciding on the structure and relational model to use                              \\
        \hline
        29th March            & 1                         & Drafting the \textit{mockup} of \textit{frontend} application                      \\
        \hline
        5th April             & 2                         & Implementation of application screens                                              \\
        \hline
        5th April             & 3                         & Implementation of necessary \textit{Smart Contracts}                               \\
        \hline
        15th April            & 1                         & Individual Presentation                                                            \\
        \hline
        30th April            & 2                         & Testing, experimental evaluation \newline including usability testing              \\
        \hline
        13th May              & 2                         & Creation and development of the poster \newline and delivery of the beta version   \\
        \hline
        28th May              & 6                         & Optimizations, completion of the report \newline and delivery of the final version \\
        \hline
    \end{tabular}
    \caption{Project Work Plan}
\end{table}




