%
%
%
\chapter{Conclusions}\label{chap:conclusions}

\dots

\section{Future Work}\label{sec:future-work}

While the SCAR project has made significant progress in the development of the DiGo Certify application, there are several areas for future work that emerged during the course of this project.
These aim to further improve the application and its usability, as well as to extend its functionality.

\begin{itemize}
    \item \textbf{User Interface Improvements:} The user interface of the DiGo Certify application could be further improved to enhance the user experience. This could include making the application more responsive, improving the layout and design of the user interface, and adding additional features to make the application more user-friendly.
    \item \textbf{Additional Features:} There are several additional features that could be added to the DiGo Certify application to enhance its functionality. For example, the application could possibilitate a institution to see all the certificates issued by them, and the status of each certificate. This would allow institutions to easily track the progress of their certificates and ensure that they are being issued in a timely manner.
    \item \textbf{Integration with IPFS:} The DiGo Certify application could be integrated with the InterPlanetary File System (IPFS) to store the certificates on a decentralized network. This would provide additional security and reliability for the certificates, as they would be stored on a distributed network of nodes rather than a single centralized server.
    \item \textbf{Better Encryption:} The encryption used to secure the certificates could be improved to make it more secure. For example, the application could use more advanced encryption algorithms to protect the certificates from unauthorized access.
    \item \textbf{Publish/Subscribe System:} The DiGo Certify application could be extended to include a publish/subscribe secure messaging system. Instead of sending emails, the application could send notifications to the institutions when a student requests a certificate, or when a certificate is issued.
\end{itemize}